---
output: moodlequiz::moodlequiz
title: Changing scales
times: 5
category: datavis
---

## Changing scales

```{r setup, include = FALSE}
library(tidyverse)
library(rlang)
library(moodlequiz)
knitr::opts_chunk$set(echo = FALSE,
                      results = "hide",
                      fig.height = 10, 
                      fig.width = 10,
                      fig.path = "",
                      fig.cap = "",
                      fig.align = "center")
```
```{r data}
cols <- colnames(diamonds)
x <- sample(c("carat", "depth", "x", "y", "z"), 1)
wrap <- sample(c("cut", "color", "clarity"), 1)
```

Using the `diamonds` dataset, complete the code below to generate the target plot below. The plot is using a log with base 10 transformation on the y-axis, a square-root transformation on the x-axis and the color is using the default viridis palette. **Only exact match with the answer will be marked correct, so make sure you entered your answer as you intended!**

```{r, echo = TRUE, results = "show"}
data(diamonds, package = "ggplot2")
str(diamonds)
```

```r
ggplot(diamonds, aes(x = `r cloze(x)`, y = price)) + 
  geom_`r cloze("hex")`() +
  facet_wrap(~`r cloze(wrap)`) +
  scale_`r cloze("y_log10")`(name = "Price ($)", labels = scales::comma) +
  scale_`r cloze("x_sqrt")`() +
  scale_`r cloze("fill")`_viridis_c()
```


```{r, results = "show"}
ggplot(diamonds, aes(x = !!sym(x), y = price)) + 
  geom_hex() +
  facet_wrap(sym(wrap)) +
  scale_y_log10(name = "Price ($)", labels = scales::comma) +
  scale_x_sqrt() +
  scale_fill_viridis_c()
```

