---
output: moodlequiz::moodlequiz
title: Changing themes
times: 5
category: datavis
---

## Theming plots

```{r set-up, include = FALSE}
library(tidyverse)
library(rlang)
library(moodlequiz)
knitr::opts_chunk$set(echo = FALSE,
                      results = "hide",
                      fig.height = 6, 
                      fig.width = 6,
                      fig.path = "",
                      fig.cap = "",
                      fig.align = "center",
                      warning = FALSE,
                      message = FALSE)
```
```{r data}
cont <- c("bill_length_mm", "bill_depth_mm", "flipper_length_mm", 
"body_mass_g")
cats <- c("species", "island", "sex")
clean_labels <- setNames(c("Bill length (mm)", "Bill depth (mm)", 
                          "Flipper length (mm)", "Body mass (g)",
                          "Species", "Island", "Sex"), c(cont, cats))
x <- sample(cont, 1)
y <- sample(setdiff(cont, x), 1)
color <- sample(cats, 1)
facet <- sample(setdiff(cats, color))
theme_args <- setdiff(names(as.list(args(theme))), c("...", ""))
ele <- c("element_text", "element_rect", "element_line")
```

For the following plot made using the `penguins` dataset, identify the theme argument names and the corresponding function to modify the look of the plot. 

```{r, echo = TRUE, results = "show"}
data(penguins, package = "palmerpenguins")
str(penguins)
```

```r
ggplot(penguins, aes(x = `r x`, y = `r y`, color = `r color`)) + 
  geom_point() +
  facet_grid(`r facet[1]` ~ `r facet[2]`) +
  labs(x = `r clean_labels[x]`, 
       y = `r clean_labels[y]`,
       color = `r clean_labels[color]`) +
  theme(`r cloze("strip.background", theme_args)` = element_rect(fill = "indianred"),
        `r cloze("strip.text", theme_args)` = element_text(color = "white"),
        `r cloze("panel.background", theme_args)` = `r cloze("element_rect", ele)`(fill = "white", color = "black"),
        `r cloze("panel.grid", theme_args)` = `r cloze("element_line", ele)`(color = "pink"),
        `r cloze("axis.title", theme_args)` = `r cloze("element_text", ele)`(size = 18),
        `r cloze("plot.title", theme_args)` = element_text(size = 24, face = "bold"))
```


```{r, results = "show"}
ggplot(penguins, aes(x = !!sym(x), y = !!sym(y), color = !!sym(color))) + 
  geom_point() +
  facet_grid(as.formula(paste0(facet[1], "~", facet[2]))) +
  labs(x = clean_labels[x], y = clean_labels[y], color = clean_labels[color], title = "Palmer Penguins") +
  theme(strip.background = element_rect(fill = "indianred"),
        strip.text = element_text(color = "white"),
        panel.background = element_rect(fill = "white",
                                        color = "black"),
        panel.grid = element_line(color = "pink"),
        axis.title = element_text(size = 18),
        plot.title = element_text(size = 24, face = "bold"))
```

---

This was a very hard one so well done if you got it right! 

You had to recognise what changed from the default in the plot (e.g. notice that the panel background is not the default grey but white instead and it has a black border). 

Since the code for the data is provided, you could have also recreated this plot by yourself and see if it matches up with the output. 
