---
output: moodlequiz::moodlequiz_cloze
title: Layer choices
times: 5
topic: datavis
---

```{r set-up, include = FALSE}
library(tidyverse)
library(rlang)
library(moodlequiz)
library(exams)
knitr::opts_chunk$set(echo = FALSE,
                      results = "hide",
                      fig.height = 4, 
                      fig.width = 5,
                      fig.path = "",
                      fig.cap = "",
                      fig.align = "center",
                      warning = FALSE,
                      message = FALSE)
```
```{r data}
dbls <- c("price", "lotsize")
counts <- c("bedrooms", "bathrms", "stories", "garagepl")
fcts <- c("driveway", "recroom", "fullbase", "gashw", "airco", "prefarea")

x1 <- sample(dbls, 1)
x2 <- sample(fcts, 1)
x3 <- c(sample(dbls, 1), sample(fcts, 1))

q1 <- sample(c("geom_point", "geom_line", "geom_label", "geom_smooth", "geom_histogram"))
q2 <- sample(c("geom_bar", "geom_line", "geom_text", "geom_path", "geom_boxplot"))
q3 <- sample(c("geom_point", "geom_line", "geom_density_2d", "geom_path", "geom_violin"))
```


Question
========
We will be using the `Housing` data from the `Ecdat` package for the following questions. The format of the data and information on the variables in the data are provided below.

```{r, echo = TRUE, results = "show"}
data(Housing, package = "Ecdat")
str(Housing)
```

* `price`: sale price of a house
* `lotsize`: the lot size of a property in square feet
* `bedrooms`: number of bedrooms
* `bathrms`: number of full bathrooms
* `stories`: number of stories excluding basement
* `driveway`: does the house has a driveway?
* `recroom`: does the house has a recreational room?
* `fullbase`: does the house has a full finished basement?
* `gashw`: does the house uses gas for hot water heating?
* `airco`: does the house has central air conditioning?
* `garagepl`: number of garage places
* `prefarea`: is the house located in the preferred neighbourhood of the city?

Choose the most appropriate `geom_*` function from the given list to visualise the following variables:

a) `r x1`: `cloze schoice(q1, "geom_histogram")`
b) `r x2`: `cloze schoice(q2, "geom_bar")`
c) `r x3[1]` and `r x3[2]` together: `cloze schoice(q3, "geom_violin")`

