---
output: moodlequiz::moodlequiz
title: Fit a simple linear model
times: 5
category: regression
---

## Fit a simple linear model

```{r set-up, include = FALSE}
library(tidyverse)
library(moodlequiz)
knitr::opts_chunk$set(echo = FALSE,
                      results = "hide")
```
```{r data}
fn <- "data-01.csv"
a <- 0
b <- sample(c(-1, 1), 1) * sample(c(0, 0.6, 0.9), 1)
dat <- data.frame(x = runif(200, -1, 1)) %>% 
  mutate(y = a + b * x + rnorm(n(), 0, 0.25)) %>% 
  mutate(across(everything(), ~round(.x, 2)))
write.csv(dat, fn, row.names = FALSE, quote = FALSE)

fit <- lm(y ~ x, data = dat)
bhats <- round(coef(fit), 4)
bpvl <- summary(fit)$coefficients[2, 4]
bsol <- c(bpvl >= 0.05, (bpvl < 0.05) & (bhats[2] > 0), (bpvl < 0.05) & (bhats[2] < 0))

opts <- c("`x` and `y` are not significantly correlated",
          "`y` increases significantly with `x`",
          "`y` decreases significantly with `x`")
```   

Using the data provided in [`r fn`](`r fn`) estimate a linear regression of
`y` on `x` and answer the following questions. _**For numerical answers, write your answer to 4 decimal places.**_

a) Which of the statement is true? `r cloze(opts[bsol], opts)`
b) What is the least squares estimate of the **intercept**? `r cloze(bhats[1])`
c) What is the least squares estimate of the **slope**? `r cloze(bhats[2])`
d) What is the **correlation** of `x` and `y`? `r cloze(round(cor(dat$x, dat$y), 4), tolerance = 0.0001)`

---

To replicate the analysis in R:

```r
dat <- read.csv("`r fn`")
fit <- lm(y ~ x, data = dat)
summary(fit)
```

It is also always good practice to visualise the data:

```r
library(ggplot2)
ggplot(dat, aes(x, y)) +
 geom_point() + 
 geom_smooth(method = "lm", se = FALSE)
```
