---
output: moodlequiz::moodlequiz_cloze
title: Multiple linear regression
times: 5
topic: regression
tolerance: 0.0001
#keep_rmd: true
---

```{r set-up, include = FALSE}
library(tidyverse)
library(moodlequiz)
library(exams)
knitr::opts_chunk$set(echo = FALSE,
                      results = "hide")

## Choose number based on below
original <- read_tsv("http://www.statsci.org/data/general/hills.txt")
fit0 <- lm(log(Time) ~ log(Climb) * log(Distance), data = original)
fit1 <- lm(log(Climb) ~ log(Distance), data = original)

betas0 <- coef(fit0)
betas1 <- coef(fit1)
df <- tibble(race_id = 1:200) %>% 
  mutate(climb = rexp(n(), 1/200),
         climb = climb / max(climb) * 7200 + 300,
         distance = exp(betas1[1] + betas1[2] * log(climb) + rnorm(n(), 0, sigma(fit1))),
         distance = distance / max(distance) * 26 + 2,
         time = exp(betas0[1] + betas0[2] * log(climb) + betas0[3] * log(distance) + 
                      betas0[4] * log(climb) * log(distance) + rnorm(n(), 0, sigma(fit0))))
# pred <- map_dfr(fivenum(original$Climb), ~{
#     res <- tibble(Distance = seq(min(original$Distance), max(original$Distance), length.out = 1000)) %>% 
#       mutate(Climb = .x)
#     res$Time <- exp(predict(fit0, res))
#     res
#   })
#   
# 
# ggplot(original, aes(Distance, Time)) +
#   geom_point(aes(fill = Climb), shape = 22) + 
#   scale_x_log10() +
#   scale_y_log10() +
#   geom_line(data = pred, aes(color = factor(Climb)))

fn <- "data-04.csv"

fit1 <- lm(log10(time) ~ log10(climb) * log10(distance), data = df)
fit2 <- lm(log10(time) ~ log10(distance), data = df)
beta1 <- round(coef(fit1), 4)
beta2 <- round(coef(fit2), 4)

write.csv(df, fn, row.names = FALSE, quote = FALSE)
```   


The data provided in [`r fn`](`r fn`) contains information about the record-winning times of 200 races. The data contains the following variables:

* `distance`: the distance covered in miles,
* `climb`: elevation climbed during the race in feet, and
* `time`: the record time for race in minutes.

The following two models are proposed:

$$\begin{align}M_1: &\log_{10}(\texttt{time}_i) = \beta_0 + \beta_1 \log_{10}(\texttt{climb}_i) + \beta_2 \log_{10}(\texttt{distance}_i) + \beta_3 \log_{10}(\texttt{climb}_i) \times \log_{10}(\texttt{distance}_i) + e_{1i},\\ M_2: & \log_{10}(\texttt{time}_i) = \gamma_0 + \gamma_1\log_{10}(\texttt{distance}_i) + e_{2i},\end{align}$$
$$$$
where $i = 1, ..., 200$ and assume $e_{1i}\sim N(0, \sigma^2), e_{2i} \sim N(0, \sigma^2)$. Fit the model using least squares method. 


a) For $M_1$, what is the least squares estimate of the following parameters to 4 decimal places? 
  * $\hat{\beta}_0 =$ `cloze beta1[1]`
  * $\hat{\beta}_1 =$ `cloze beta1[2]`
  * $\hat{\beta}_2 =$ `cloze beta1[3]`
  * $\hat{\beta}_3 =$ `cloze beta1[4]`
b) What is the sum of the squares of the residuals for $M_1$ and $M_2$, respectively, to 4 decimal places?  
$M_1$: `cloze round(sum(fit1$residuals^2), 4)` and $M_2$: `cloze round(sum(fit2$residuals^2), 4)`.
c) You want to draw a scatter plot with the fitted model $M_2$ superimposed on it like the plot below.
```{r, fig.show="hold"}
library(ggplot2)
ggplot(df, aes(distance, time)) +
  geom_point() + 
  geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
  scale_x_log10() + 
  scale_y_log10()
```

Complete the code below to draw the above plot.
```r
library(ggplot2)
ggplot(df, aes(distance, time)) +
  geom_point() + 
  geom_`cloze "smooth"`(method = lm, formula = y ~ x, se = FALSE) +
  `cloze "scale_x_log10"`() + 
  scale_y_log10()
```

---

The two models are fitted in R like below:

```r
df <- read.csv("`r fn`")
fit1 <- lm(log10(time) ~ log10(climb) * log10(distance), data = df)
fit2 <- lm(log10(time) ~ log10(distance), data = df)
coef(fit1)
sum(fit1$residuals^2)
sum(fit2$residuals^2)
```

When superimposing the model, you need the $\log_{10}$ scale transformations like below.

```r
library(ggplot2)
ggplot(df, aes(distance, time)) +
  geom_point() + 
  geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
  scale_x_log10() + 
  scale_y_log10()
```

